\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}
  [\titlerule]

\begin{document}

%====================
% HEADER
%====================
\begin{center}
    {\LARGE \textbf{Shakibul Hasan}}\\
    \vspace{2pt}
    \textbf{Web Development Enthusiast}
\end{center}

\vspace{6pt}

\begin{tabularx}{\textwidth}{X X}
Email: \href{mailto:ushakibul60@gmail.com}{ushakibul60@gmail.com} &
Phone: 01861380367 \\
Nationality: Bangladeshi &
Sex: Male \\
\end{tabularx}

%====================
% ABOUT
%====================
\section*{About Me}
I am Shakibul Hasan, a passionate Web Development Enthusiast who enjoys building
clean, responsive, and user-friendly websites. I love learning new technologies
and improving my problem-solving skills.

%====================
% PERSONAL & FAMILY
%====================
\section*{Personal \& Family Information}

\textbf{Personal Information}
\begin{itemize}[leftmargin=*]
    \item Name: Shakibul Hasan
    \item Email: ushakibul60@gmail.com
    \item Phone: 01861380381
    \item Nationality: Bangladeshi
    \item Sex: Male
\end{itemize}

\textbf{Family Information}
\begin{itemize}[leftmargin=*]
    \item Father: Shirajul Islam
    \item Mother: Buley Bagum
\end{itemize}

%====================
% EDUCATION
%====================
\section*{Education}
\begin{tabularx}{\textwidth}{|l|X|c|c|}
\hline
\textbf{Level} & \textbf{Institute} & \textbf{Year} & \textbf{Result} \\
\hline
SSC & Ram Ballavpur High School & 2019 & 5.00 \\
\hline
HSC & Noakhali Government College & 2021 & 5.00 \\
\hline
Honours / Bachelor's & Premier University & Running & CGPA: X.XX \\
\hline
\end{tabularx}

%====================
% EXTRA-CURRICULAR ACTIVITIES
%====================
\section*{Extra-Curricular Activities}
\begin{itemize}[leftmargin=*]
    \item Served as a Volunteer at Himu Utsob
    \item Organizer for Himu Utsob 2.0
    \item Executive Member of the Computer Club, Premier University
    \item Former Rover Scout at Noakhali Government College
    \item Founding Member of the PUC Blood Bank
\end{itemize}


%====================
% PROJECTS & PROFESSIONAL SKILLS
%====================
\section*{Projects \& Professional Skills}

\begin{itemize}[leftmargin=*]
    \item \textbf{Racing Game} — Fun project using Unity Game Engine with C\#; demonstrates programming and game development interest.
    \item \textbf{Project Support Experience} — Exposure to maintaining records, logs, correspondence, and documentation standards.
    \item \textbf{Office Administration Skills} — Familiar with MS Office (Word, Excel, PowerPoint) and Google Workspace (Drive, Docs, Sheets).
    \item \textbf{Technical Skills} — HTML, CSS, JavaScript, C, C++, Java.
\end{itemize}



%====================
% WORK EXPERIENCE
%====================
\section*{Work Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Sales Representative, Local Retail Store} — Assisted customers, managed inventory, and handled daily sales operations.
    \item \textbf{IT Administrator, Local ISP} — Managed network setup, provided technical support to clients, and maintained server and network systems.
\end{itemize}

\textbf{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Web Development:} HTML, CSS, JavaScript
    \item \textbf{Programming Languages:} C, C++, Java
    \item \textbf{Tools \& Platforms:} Unity Game Engine (C\#), MS Office, Google Workspace
\end{itemize}


%====================
% LANGUAGES
%====================
\section*{Languages}
\begin{itemize}[leftmargin=*]
    \item Bangla — Native
    \item English — Fluent
    \item German — Basic proficiency (Reading and Listening)
\end{itemize}



%====================
% HOBBIES
%====================
\section*{Hobbies}
\begin{itemize}[leftmargin=*]
    \item Playing Games
    \item Event Management
    \item Watching Movies
\end{itemize}


%====================
% FOOTER
%====================
\vfill
\begin{center}
{\small © 2026 Shakibul Hasan — All Rights Reserved}
\end{center}

\end{document}
